### 2010-06-28 paper/IIWAS2010/content/system_arch.tex
Changes to the system arch. section

Morpheus requires a realm-based ontology that contains categories of a
particular realm of interest. For example, the realm-ontology \textit{Automotive}
contains categories that are relevant to the \textit{automotive} realm. In
addition, every leaf node in the category ontology is associated with a corpus of words
that belongs to that category.

For ontology construction Morpheus uses the Wikipedia pages, categories,
and the WordNet synset heterarchy. This approch is motivated from
YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
from the DBpedia categories, which are extracted from 
the Wikipedia pages\cite{Bizer2009}. Then we grab all the neighboring categories
using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
the category's parents, its children, and its 
children's other parents using the DBpedia ontology properties \textit{broader}
and \textit{narrower}. Once the blanket is ready, it grabs all parent categories
of the categories in the blanket till it reaches root. Once we have the
categories belongs to a particular domain, we associate them with WordNet synsets
using an algorithm similar to YAGO\cite{Suchanek2009phd}. We determine head noun in the
category name and search for it in the WordNet synsets.
Those Wikipedia categories having no WordNet match are ignored in the our realm
ontology. In fact we uses the WordNet synset heterarchy as the backbone of the   
realm ontology.

@@

To answer a regular user's query, a \textit{candidate
SSQ}, Morpheus finds similar SSQs that belong to QRMs the Morpheus data store (a
\textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
with a qualified SSQ. For the SSQ similarity, we
consider the SSQ components such as query-realm, input
terms and output terms, and their assigned categories or classes. The,
\textit{category divergence} of two categories characteristics their 
similarity based on an ontology class heterarchy. 
It is motivated by the concept of multiple
dispatch in CLOS and Dylan programming for generic function \emph{type} matches.

We consider the category match as a type match and we use 
\emph{category divergence} to calculate the relevance between 
the candiate SSQ and a qualified SSQ. Each qualified SSQ will 
have input terms, output terms, and associated classes, and one realm. 
For the candidate SSQ, the relevant category for input terms 
are determined from the ontology corpora [section \ref{sec:ontology_corpora}]. The relevance of a qualified SSQ to the candidate SSQ is 
determined by aggregating the divergence measure of categories 
associated with them. In addition, we order QRMs in the data store 
by descreasing relevance. The order provides a ranking for the results 
to the user. The following subsection describes \emph{category divergence} 
in detail.

>>>>

Morpheus requires a realm-based ontology that contains categories of a
particular realm of interest. For example, the realm-ontology \textit{Automotive}
contains categories that are relevant to the automotive realm. In
addition, every leaf node in the category ontology is associated with a corpus of words
that belongs to that category.

For ontology construction Morpheus uses the Wikipedia pages, categories,
and the WordNet synset heterarchy. This approch is motivated from
YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
from the DBpedia categories\cite{Bizer2009}. Then we grab all the neighboring categories using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
the category's parents, its children, and its 
children's other parents using the DBpedia ontology properties \textit{broader}
and \textit{narrower}. Once the blanket is ready, it grabs all parent categories
of the categories in the blanket till it reaches root. Once we have the
categories belongs to a particular domain, we associate them with WordNet synsets
using an algorithm similar to YAGO\cite{Suchanek2009phd}. We determine head noun in the
category name and search for it in the WordNet synsets.
Those Wikipedia categories having no WordNet match are ignored in the our realm
ontology. In addition, we uses the WordNet synset heterarchy relationships for building the ontologcial structure.

@@

To answer a regular user's query, a \textit{candidate
SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
with a qualified SSQ. For the SSQ similarity, we
consider the SSQ components such as query-realm, input
terms and output terms, and their assigned categories or classes [To be changed]. The,
\textit{category divergence} of two categories characteristics their 
similarity based on an ontology class heterarchy. 
It is motivated by the concept of multiple
dispatch in CLOS and Dylan programming for generic function \emph{type} matches.

We consider the category match as a type match and we use 
\emph{category divergence} to calculate the relevance between 
the candiate SSQ and a qualified SSQ. Each qualified SSQ will 
have input terms, output terms[what do we do with this??], and associated classes, and one realm. 
For the candidate SSQ, the relevant category for input terms 
are determined from the ontology corpora [section \ref{sec:ontology_corpora}]. We match QRMs that belong to the same \emph{realm} of the candidate SSQ. The relevance of a qualified SSQ to the candidate SSQ is 
determined by aggregating the divergence measure of input-term-categories 
associated with them. In addition, we order QRMs in the data store 
by descreasing relevance. The order provides a ranking for the results 
to the user. The following subsection describes \emph{category divergence} 
in detail.
